Verifying Demonstrations

### 2021-06-16 paper/system-model.tex
Merges system model into definitions section
Just say we want Sybil proofness; no more, no less.

\section{System model}%
\label{system-model}

To set the stage, we will now describe our system model including
assumptions and a summary of the desired properties for crowd
counting% and the adversary model
.

\subsection{Model and assumptions}%
\label{assumptions}

Throughout this paper, each time we refer to a participant, such as Alice, we 
actually mean a personal device that can perform cryptographic operations and 
communicate with other local devices on Alice's behalf.
Furthermore, we assume that each participant has a digital identity certificate signed 
by \iac{CA}\footnote{%
  We note that any system that prevents Sybil attacks~\cite{SybilAttack} will 
  do.
  The \ac{CA} can be centralized or decentralized, but as 
  \textcite{SybilAttack} points out, the \ac{CA} must be \emph{logically 
    centralized} to prevent Sybil attacks.
 } that ensures a one-to-one mapping between an identity and a cryptographic 
key\footnote{%
  For every physical person there exists at most one valid digital certificate.
}.

>>>>

\subsection{System model and assumptions}%
\label{assumptions}

Throughout this paper, each time we refer to a participant, such as Alice, we 
actually mean a personal device that can perform cryptographic operations and 
communicate with other local devices on Alice's behalf.
Furthermore, we assume that each participant has a digital identity certificate signed 
by \iac{CA}\footnote{%
  We note that any system that prevents Sybil attacks~\cite{SybilAttack} will 
  do.
} that ensures a one-to-one mapping between an identity and a cryptographic 
key\footnote{%
  For every physical person there exists at most one valid digital certificate.
}.
